---
title: "ECON 573 Research Paper"
author: "Siddhartha Vanam"
date: "11/5/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Necessary Libraries
```{r test1, echo=FALSE}
library(tidyverse)
library(fGarch)
library(fredr)
library(quantmod)
library(tidyquant)
```

# Research Question in Discussion: Using the Garch Model to explain volatility of `VHT` and `VDE`  that represent Sector `Healthcare` and `Energy` (daily).

```{r}
vht = tq_get("VHT", 
        from = '2005-01-01',
        to = "2021-01-01",warnings = FALSE)
```


```{r}
vde = tq_get("VDE", 
        from = '2005-01-01',
        to = "2021-01-01",warnings = FALSE)
```


```{r}
#Vanguard's S&P 500
sp = tq_get("^GSPC", 
        from = '2005-01-01',
        to = "2021-01-01",warnings = FALSE)
```


```{r}
vix = tq_get("^VIX", 
        from = '2005-01-01',
        to = "2021-01-01",warnings = FALSE)
```




```{r}
#might have to prefix the columns before we merge with the respective symbol

head(vht)
head(vde)
head(sp)
sample(vix)
```

# Getting Data for the Macro Indicator
```{r}
api_key = "dde5ad634e39b6e288c9a2ebec181e58"
fredr_set_key(api_key)

#Daily Indicators are as Follows:
crude_oil_prices = fredr(
  series_id = "DCOILBRENTEU",
  observation_start = as.Date("2005-01-01"),
  observation_end = as.Date("2021-01-01"))[,c(1,3)]

intl_trade_weight_dol = fredr(
  series_id = "DTWEXBGS",
  observation_start = as.Date("2005-01-01"),
  observation_end = as.Date("2021-01-01"))[,c(1,3)]

yield_2yr = fredr(
  series_id = "DGS2",
  observation_start = as.Date("2005-01-01"),
  observation_end = as.Date("2021-01-01"))[,c(1,3)]

#Rename Dataframes before merging
names(crude_oil_prices) = c("date", "crude_oil_price_value")
names(intl_trade_weight_dol) = c("date", "intl_trade_weight_dol_value")
names(yield_2yr) = c("date", "yield_2yr_value")

# Forward Filled Values for Weekly Data
crude_oil_prices = crude_oil_prices %>%
  complete(date = seq.Date(min(date), max(date), by="day")) %>%
  fill(crude_oil_price_value, .direction = "up")

intl_trade_weight_dol = intl_trade_weight_dol %>%
  complete(date = seq.Date(min(date), max(date), by="day")) %>%
  fill(intl_trade_weight_dol_value, .direction = "up")

yield_2yr = yield_2yr %>%
  complete(date = seq.Date(min(date), max(date), by="day")) %>%
  fill(yield_2yr_value, .direction = "up")

#Merging Data
daily_indicators = full_join(crude_oil_prices, intl_trade_weight_dol) %>% full_join(yield_2yr)
```

```{r}
#Weekly Indicators are as follows:
intl_job_claims = fredr( 
  series_id = "ICSA",
  observation_start = as.Date("2005-01-01"),
  observation_end = as.Date("2021-01-01"))[,c(1,3)]

chifed_nfci = fredr( 
  series_id = "NFCI",
  observation_start = as.Date("2005-01-01"),
  observation_end = as.Date("2021-01-01"))[,c(1,3)]

m.1 = fredr( 
  series_id = "M1SL",
  observation_start = as.Date("2005-01-01"),
  observation_end = as.Date("2021-01-01"))[,c(1,3)]

fed_bal = fredr( 
  series_id = "WALCL",
  observation_start = as.Date("2005-01-01"),
  observation_end = as.Date("2021-01-01"))[,c(1,3)]

treas_gen_acct = fredr( 
  series_id = "WDTGAL",
  observation_start = as.Date("2005-01-01"),
  observation_end = as.Date("2021-01-01"))[,c(1,3)]

#Rename Dataframes before merging
names(intl_job_claims) = c("date", "intl_job_claims_value")
names(chifed_nfci) = c("date", "chifed_nfci_value")
names(m.1) = c("date", "m.1_value")
names(fed_bal) = c("date", "fed_bal_value")
names(treas_gen_acct) = c("date", "treas_gen_acct_value")

# Forward Filled Values for Weekly Data
intl_job_claims = intl_job_claims %>%
  complete(date = seq.Date(min(date), max(date), by="day")) %>%
  fill(intl_job_claims_value, .direction = "up")

chifed_nfci = chifed_nfci %>%
  complete(date = seq.Date(min(date), max(date), by="day")) %>%
  fill(chifed_nfci_value, .direction = "up")

m.1 = m.1 %>%
  complete(date = seq.Date(min(date), max(date), by="day")) %>%
  fill(m.1_value, .direction = "up")

fed_bal = fed_bal %>%
  complete(date = seq.Date(min(date), max(date), by="day")) %>%
  fill(fed_bal_value, .direction = "up")

treas_gen_acct = treas_gen_acct %>%
  complete(date = seq.Date(min(date), max(date), by="day")) %>%
  fill(treas_gen_acct_value, .direction = "up")

#Merging Weekly Indicators
weekly_indicators = full_join(intl_job_claims, chifed_nfci) %>% full_join(chifed_nfci) %>% full_join(m.1) %>% full_join(fed_bal) %>% full_join(treas_gen_acct)

weekly_indicators
```

```{r}
#Monthly Indicators are as follows:
cpi = fredr( 
  series_id = "USACPIALLMINMEI",
  observation_start = as.Date("2005-01-01"),
  observation_end = as.Date("2021-01-01"))[,c(1,3)]

ur = fredr(
  series_id = "UNRATE",
  observation_start = as.Date("2005-01-01"),
  observation_end = as.Date("2021-01-01"))[,c(1,3)]

#Rename Dataframes before merging
names(cpi) = c("date", "cpi_value")
names(ur) = c("date", "ur_value")

# Forward Filled Values for Monthly Data
cpi = cpi %>%
  complete(date = seq.Date(min(date), max(date), by="day")) %>%
  fill(cpi_value, .direction = "up")

ur = ur %>%
  complete(date = seq.Date(min(date), max(date), by="day")) %>%
  fill(ur_value, .direction = "up")

#Merging Monthly Indicators
monthly_indicators = full_join(ur, cpi)
monthly_indicators
```

```{r}
final_indicator_df = full_join(daily_indicators, weekly_indicators) %>%          full_join(monthly_indicators) %>%
  fill(c("crude_oil_price_value", "intl_trade_weight_dol_value", "yield_2yr_value",
         "chifed_nfci_value", "intl_job_claims_value", "m.1_value", "fed_bal_value",
         "treas_gen_acct_value", "ur_value", "cpi_value"), .direction = "up") %>%
  
# Fill Down for the most recent dates
  fill(c("crude_oil_price_value", "intl_trade_weight_dol_value", "yield_2yr_value", "intl_job_claims_value", "fed_bal_value", "treas_gen_acct_value"), .direction = "down")

# Check to make sure that there are no more NAs in each column
final_indicator_df %>% summarise_all(~ sum(is.na(.)))
```


+ Type of Problem: **Regression**
- Linear Regression
- Lasso/ Ride/ Elastic Net (Only Have to pick 1)

*Create Factor Importance Plots*
- Regression Trees
- Random Forests
- Boosting

- ~~SVM~~
- ~~kNN~~

# Requirements

+ 15 pages long

# Parts

+ ~~Research Question~~
+ ~~Data~~
+ Methodology
  + Assumptions
  + Unique
  + Interpretability
  + Bias/ Variance Tradeoff in parameter selection
+ Results



