---
title: "ECON 573 Research Paper"
author: "Siddhartha Vanam"
date: "11/5/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Necessary Libraries
```{r test1, echo=FALSE}
library(tidyverse)
library(fGarch)
library(fredr)
library(quantmod)
library(tidyquant)
```

# Research Question in Discussion: Using the Garch Model to explain volatility of `VHT` and `VDE`  that represent Sector `Healthcare` and `Energy` (daily).

```{r}
vht = tq_get("VHT", 
        from = '2010-01-01',
        to = "2021-11-01",warnings = FALSE)
vde = tq_get("VDE", 
        from = '2005-01-01',
        to = "2021-01-01",warnings = FALSE)
#Vanguard's S&P 500
voo = tq_get("VOO", 
        from = '2005-01-01',
        to = "2021-01-01",warnings = FALSE)

vix = tq_get("^VIX", 
        from = '2010-01-01',
        to = "2021-11-01",warnings = FALSE)
head(vht)
head(vde)
head(voo)
vix
```

# Getting Data for the Macro Indicator
```{r}
api_key = "dde5ad634e39b6e288c9a2ebec181e58"
#IR, UR, CPI
fredr_set_key(api_key)
ur = fredr(
  series_id = "UNRATE",
  observation_start = as.Date("2005-01-01"),
  observation_end = as.Date("2021-01-01")
)

```


+ Type of Problem: **Regression**
- Linear Regression
- Lasso/ Ride/ Elastic Net
- Regression Trees
- Random Forests
- Boosting
- SVM
- kNN

# Requirements

+ 15 pages long

# Parts

+ Research Question
+ Data
+ Methodology
  + Assumptions
  + Unique
  + Interpretability
  + Bias/ Variance Tradeoff in parameter selection
+ Results



