---
title: "ECON 573 Research Paper"
author: "Siddhartha Vanam"
date: "11/5/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Necessary Libraries
```{r test1, echo=FALSE}
library(tidyverse)
library(tseries)
library(fredr)
library(quantmod)
library(tidyquant)
library(fGarch)
```

# Research Question in Discussion: Using the Garch Model to explain volatility of `VHT` and `VDE`  that represent Sector `Healthcare` and `Energy` (daily).

```{r}
vht = tq_get("VHT", 
        from = '2006-01-01',
        to = "2021-01-01",warnings = FALSE)
```


```{r}
vde = tq_get("VDE", 
        from = '2006-01-01',
        to = "2021-01-01",warnings = FALSE)
```


```{r}
#S&P 500
sp = tq_get("^GSPC", 
        from = '2006-01-01',
        to = "2021-01-01",warnings = FALSE)
sp = sp[, c(2,8)]
sp
i <- 2
while(i<3776){
  sp[i, "adjusted_detr"] = sp$adjusted[i]-sp$adjusted[i-1]
  i <- i + 1
}
sp <- drop(sp[-c(1,3776),])
adf.test(sp$adjusted_detr)

```


```{r}
vix = tq_get("^VIX", 
        from = '2006-01-01',
        to = "2021-01-01",warnings = FALSE)
```


```{r}
#might have to prefix the columns before we merge with the respective symbol
head(vht)
head(vde)
head(sp)
sample(vix)
```

# Getting Data for the Macro Indicator
```{r}
api_key = "dde5ad634e39b6e288c9a2ebec181e58"
fredr_set_key(api_key)

#Daily Indicators are as Follows:
crude_oil_prices = fredr(
  series_id = "DCOILBRENTEU",
  observation_start = as.Date("2006-01-01"),
  observation_end = as.Date("2021-01-01"))[,c(1,3)]

intl_trade_weight_dol = fredr(
  series_id = "DTWEXBGS",
  observation_start = as.Date("2006-01-01"),
  observation_end = as.Date("2021-01-01"))[,c(1,3)]
yield_2yr = fredr(
  series_id = "DGS2",
  observation_start = as.Date("2006-01-01"),
  observation_end = as.Date("2021-01-01"))[,c(1,3)]
#Rename Dataframes before merging
names(crude_oil_prices) = c("date", "crude_oil_price_value")
names(intl_trade_weight_dol) = c("date", "intl_trade_weight_dol_value")
names(yield_2yr) = c("date", "yield_2yr_value")
```

```{r}
# Forward Filled Values for Weekly Data
crude_oil_prices = crude_oil_prices %>%
  complete(date = seq.Date(min(date), max(date), by="day")) %>%
  fill(crude_oil_price_value, .direction = "down")
intl_trade_weight_dol = intl_trade_weight_dol %>%
  complete(date = seq.Date(min(date), max(date), by="day")) %>%
  fill(intl_trade_weight_dol_value, .direction = "down")
yield_2yr = yield_2yr %>%
  complete(date = seq.Date(min(date), max(date), by="day")) %>%
  fill(yield_2yr_value, .direction = "down")
```


```{r}
#diff of daily
i <- 3
while(i<5479){
  crude_oil_prices[i, "detr_crude_oil_prices"] = crude_oil_prices$crude_oil_price_value[i]-crude_oil_prices$crude_oil_price_value[i-1]
  i <- i + 1
}
crude_oil_prices <- drop(crude_oil_prices[-c(1,2,5479),])
adf.test(crude_oil_prices$detr_crude_oil_prices)

i <- 2
while(i<5479){
  intl_trade_weight_dol[i, "detr_intl_dol"] = intl_trade_weight_dol$intl_trade_weight_dol_value[i]-intl_trade_weight_dol$intl_trade_weight_dol_value[i-1]
  i <- i + 1
}
intl_trade_weight_dol <- drop(intl_trade_weight_dol[-c(1,5479),])
adf.test(intl_trade_weight_dol$detr_intl_dol)

i <- 2
while(i<5479){
  yield_2yr[i, "detr_yield"] = yield_2yr$yield_2yr_value[i]-yield_2yr$yield_2yr_value[i-1]
  i <- i + 1
}
yield_2yr <- drop(yield_2yr[-c(1, 2, 5479),])
adf.test(yield_2yr$detr_yield)

#Merging Data
daily_indicators = full_join(crude_oil_prices, intl_trade_weight_dol) %>% full_join(yield_2yr)
```



```{r}
#Weekly Indicators are as follows:
intl_job_claims = fredr( 
  series_id = "ICSA",
  observation_start = as.Date("2005-12-01"),
  observation_end = as.Date("2021-01-01"))[,c(1,3)]

chifed_nfci = fredr( 
  series_id = "NFCI",
  observation_start = as.Date("2005-12-01"),
  observation_end = as.Date("2021-01-01"))[,c(1,3)]
m.1 = fredr( 
  series_id = "M1SL",
  observation_start = as.Date("2006-01-01"),
  observation_end = as.Date("2021-01-01"))[,c(1,3)]
fed_bal = fredr( 
  series_id = "WALCL",
  observation_start = as.Date("2005-12-01"),
  observation_end = as.Date("2021-01-01"))[,c(1,3)]
treas_gen_acct = fredr( 
  series_id = "WDTGAL",
  observation_start = as.Date("2005-12-01"),
  observation_end = as.Date("2021-01-01"))[,c(1,3)]

#Rename Dataframes before merging
names(intl_job_claims) = c("date", "intl_job_claims_value")
names(chifed_nfci) = c("date", "chifed_nfci_value")
names(m.1) = c("date", "m.1_value")
names(fed_bal) = c("date", "fed_bal_value")
names(treas_gen_acct) = c("date", "treas_gen_acct_value")

```

```{r}
#diff of weekly
i <- 2
while(i<788){
  chifed_nfci[i, "chifed_nfci_detrended"] = chifed_nfci$chifed_nfci_value[i]-chifed_nfci$chifed_nfci_value[i-1]
  i <- i + 1
}
chifed_nfci <- drop(chifed_nfci[-c(1,788),])
adf.test(chifed_nfci$chifed_nfci_detrended)

i <- 2
while(i<181){
  m.1[i, "m.1_detrended"] = m.1$m.1_value[i]-m.1$m.1_value[i-1]
  i <- i + 1
}
m.1 <- drop(m.1[-c(1,181),])
adf.test(m.1$m.1_detrended)

i <- 2
while(i<787){
  fed_bal[i, "fed_bal_detrended"] = fed_bal$fed_bal_value[i]-fed_bal$fed_bal_value[i-1]
  i <- i + 1
}  
fed_bal <- drop(fed_bal[-c(1,787),])
adf.test(fed_bal$fed_bal_detrended)

i <- 2
while(i<787){
  treas_gen_acct[i, "treas_gen_acct_detrended"] = treas_gen_acct$treas_gen_acct_value[i]-treas_gen_acct$treas_gen_acct_value[i-1]
  i <- i + 1
}
 treas_gen_acct <- drop( treas_gen_acct[-c(1,787),])
adf.test( treas_gen_acct$treas_gen_acct_detrended)
```



```{r}
# Forward Filled Values for Weekly Data
intl_job_claims = intl_job_claims %>%
  complete(date = seq.Date(min(date), max(date), by="day")) %>%
  fill(intl_job_claims_value, .direction = "down")
chifed_nfci = chifed_nfci %>%
  complete(date = seq.Date(min(date), max(date), by="day")) %>%
  fill(chifed_nfci_detrended, .direction = "down")
m.1 = m.1 %>%
  complete(date = seq.Date(min(date), max(date), by="day")) %>%
  fill(m.1_detrended, .direction = "down")
fed_bal = fed_bal %>%
  complete(date = seq.Date(min(date), max(date), by="day")) %>%
  fill(fed_bal_detrended, .direction = "down")
treas_gen_acct = treas_gen_acct %>%
  complete(date = seq.Date(min(date), max(date), by="day")) %>%
  fill(treas_gen_acct_detrended, .direction = "down")

#Merging Weekly Indicators
weekly_indicators = full_join(intl_job_claims, chifed_nfci) %>% full_join(chifed_nfci) %>% full_join(m.1) %>% full_join(fed_bal) %>% full_join(treas_gen_acct)
weekly_indicators
```


```{r}
#Monthly Indicators are as follows:
cpi = fredr( 
  series_id = "USACPIALLMINMEI",
  observation_start = as.Date("2006-01-01"),
  observation_end = as.Date("2021-01-01"))[,c(1,3)]
ur = fredr(
  series_id = "UNRATE",
  observation_start = as.Date("2006-01-01"),
  observation_end = as.Date("2021-01-01"))[,c(1,3)]

#Rename Dataframes before merging
names(cpi) = c("date", "cpi_value")
names(ur) = c("date", "ur_value")

```

```{r}
#diff of monthly
i <- 2
while(i<181){
  cpi[i, "cpi_detr"] = cpi$cpi_value[i]-cpi$cpi_value[i-1]
  i <- i + 1
}  
cpi <- drop(cpi[-c(1,181),])
adf.test(cpi$cpi_detr)

i <- 2
while(i<181){
  ur[i, "ur_detr"] = ur$ur_value[i]-ur$ur_value[i-1]
  i <- i + 1
}
ur <- drop(ur[-c(1,181),])
adf.test( ur$ur_detr)
```


```{r}
# Forward Filled Values for Monthly Data
cpi = cpi %>%
  complete(date = seq.Date(min(date), max(date), by="day")) %>%
  fill(cpi_detr, .direction = "down")
ur = ur %>%
  complete(date = seq.Date(min(date), max(date), by="day")) %>%
  fill(ur_detr, .direction = "down")

#Merging Monthly Indicators
monthly_indicators = full_join(ur, cpi)
monthly_indicators
final_indicator_df = full_join(daily_indicators, weekly_indicators) %>%          full_join(monthly_indicators) %>%
  fill(c("detr_crude_oil_prices", "detr_intl_dol", "detr_yield",
         "chifed_nfci_detrended", "intl_job_claims_value", "m.1_detrended", "fed_bal_detrended", "treas_gen_acct_detrended", "ur_detr", "cpi_detr"), .direction = "down") %>%
  
# Fill Down for the most recent dates
  fill(c("detr_crude_oil_prices", "detr_intl_dol", "detr_yield", "intl_job_claims_value", "fed_bal_detrended", "treas_gen_acct_detrended"), .direction = "down")

# Check to make sure that there are no more NAs in each column
final_indicator_df %>% summarise_all(~ sum(is.na(.)))
final_indicator_df <- drop(final_indicator_df[-c(1:29),])
```

#VHT FGarch
```{r}
vht['dailyReturn'] = (vht$close - vht$open)/ vht$open
holdIt = data.frame(vht$date, vht$dailyReturn)
rownames(holdIt) <- holdIt$vht.date
holdIt$vht.date <- NULL
x.vec = as.xts(holdIt)
fit <- garchFit(~ garch(1,1), data = x.vec, trace = FALSE)
volvht <- volatility(fit)
volvht <- xts(volvht, order.by = index(x.vec))
plot(volvht)
```

#VDE FGarch
```{r}
vde['dailyReturn'] = (vde$close - vde$open)/ vde$open
holdIt2 = data.frame(vde$date, vde$dailyReturn)
rownames(holdIt2) <- holdIt2$vde.date
holdIt2$vde.date <- NULL
x.vec2 = as.xts(holdIt2)
fit2 <- garchFit(~ garch(1,1), data = x.vec2, trace = FALSE)
volvde <- volatility(fit2)
volvde <- xts(volvde, order.by = index(x.vec2))
plot(volvde)
```

```{r}
vol.vde_df <- data.frame(date = as.Date(index(volvde)), 
                    coredata(volvde))
final_merged_vde <- merge(final_indicator_df, vol.vde_df, by = "date")
final_merged_vde = merge(final_merged_vde, sp, by = "date")
colnames(final_merged_vde)[13] = "adj_vde.close"
final_merged_vde <- final_merged_vde[-c(2,4,6,9,11,13,15,17,19,22)]


vol.vht_df <- data.frame(date = as.Date(index(volvht)), 
                    coredata(volvht))
final_merged_vht <- merge(final_indicator_df, vol.vht_df, by = "date")
final_merged_vht = merge(final_merged_vht, sp, by = "date")
colnames(final_merged_vht)[13] = "adj_vht.close"
final_merged_vht <- final_merged_vht[-c(2,4,6,9,11,13,15,17,19,22)]
```

```{r}
final_merged_vde %>% summarise_all(~ sum(is.na(.)))
final_merged_vht %>% summarise_all(~ sum(is.na(.)))
```

# Train- Test Split the Data
```{r}
y.vol_vde_train = final_merged_vde[1:1888,12]
y.vol_vde_test = final_merged_vde[1889:3776,12]

x_vde = final_merged_vde[,-c(1, 12)]
train_vde= final_merged_vde[1:1888,-1]
test_vde = final_merged_vde[1889:3776,-1]
colnames(final_merged_vde)


y.vol_vht_train = final_merged_vht[1:1888,12]
y.vol_vht_test = final_merged_vht[1889:3776,12]

x_vht = final_merged_vht[,-c(1, 12)]
train_vht= final_merged_vht[1:1888,-1]
test_vht = final_merged_vht[1889:3776,-1]
```



# Elastic Net Regression (VDE)
```{r}
library(caret) #Train and Validate Machine Learning Methods
library(glmnet) #Ridge, Lasso, and Elastic Net
```

## VDE
```{r}
elasticnetControl.vde = trainControl(## 5-fold CV
                            method = "repeatedcv",
                            number = 5,
                            ## repeated 5 times
                            repeats = 5) 

#Fit Elastic net to training data, and cross-validate tuning parameters alpha and lambda on l2 and l1 penalties, respectively
enetfit.vde = train(coredata.volvde. ~ ., data = train_vde, 
                 method = "glmnet", 
                 metric = "RMSE",
                 trControl = elasticnetControl.vde,
                 na.action = na.exclude)

enetpreds = predict(enetfit.vde$finalModel, #Use trained model
                   newx = as.matrix(test_vde[,2:length(test_vde[1,])]), #Predict with X variables, transformed to matrix
                   s = enetfit.vde$bestTune$lambda) #Choose the lambda parameter based on CV

enetfit.vde #Display cross validation results
```

```{r}
stats::predict(enetfit.vde$finalModel, type = "coefficients", s = enetfit.vde$bestTune$lambda)
```

## VHT
```{r}
elasticnetControl.vht = trainControl(## 5-fold CV
                            method = "repeatedcv",
                            number = 5,
                            ## repeated 5 times
                            repeats = 5) 

#Fit Elastic net to training data, and cross-validate tuning parameters alpha and lambda on l2 and l1 penalties, respectively
enetfit.vht = train(coredata.volvht. ~ ., data = train_vht, 
                 method = "glmnet", 
                 metric = "RMSE",
                 trControl = elasticnetControl.vht,
                 na.action = na.exclude)

enetpreds = predict(enetfit.vht$finalModel, #Use trained model
                   newx = as.matrix(test_vht[,2:length(test_vht[1,])]), #Predict with X variables, transformed to matrix
                   s = enetfit.vht$bestTune$lambda) #Choose the lambda parameter based on CV

enetfit.vht #Display cross validation results
```

```{r}
stats::predict(enetfit.vht$finalModel, type = "coefficients", s = enetfit.vht$bestTune$lambda)
```


```{r}
# predictions<-data.frame(fqdatest[,1],enetpreds,rfpreds)
# colnames(GDPpredictions)<-c("GDPgrowth","ElasticNet","RandomForest")
# GDPforecasts<-window(ts(GDPpredictions,frequency=4,start=c(2010,1)),end=c(2020,1))
# 
# autoplot(GDPforecasts)+ggtitle("GDP growth and forecasts from Random Forest and Elastic Net Methods",
#                               subtitle="2020Q2 removed because drop distorts the scale")
```


+ Type of Problem: **Regression**
- Linear Regression
- Lasso/ Ride/ Elastic Net 

*Create Factor Importance Plots*
- Regression Trees
- Random Forests
- Boosting

- ~~SVM~~
- ~~kNN~~

# Requirements

+ 15 pages long

# Parts

+ ~~Research Question~~
+ ~~Data~~
+ Methodology
  + Assumptions
  + Unique
  + Interpretability
  + Bias/ Variance Tradeoff in parameter selection
+ Results



